\documentclass[10pt,journal,compsoc]{IEEEtran}

\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\usepackage{array}
\usepackage{url}
\usepackage{color}
\usepackage{booktabs}
\usepackage{float}
\usepackage{subfig}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{overpic}
\usepackage{amsfonts}
\usepackage{xcolor,colortbl}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{enumitem}
\usepackage{placeins}

\definecolor{Gray}{gray}{.90}

\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
\newcommand{\etal}{\textit{et al}.}
\newcommand{\ie}{\textit{i}.\textit{e}.}
\newcommand{\eg}{\textit{e}.\textit{g}.}
\newcommand{\etc}{\textit{etc}.}

% subfigure label format handled by subfig package

\ifCLASSINFOpdf
\else
\fi

\usepackage[bookmarks,colorlinks,linkcolor=black, anchorcolor=black, citecolor=black, urlcolor=black]{hyperref}
\hyphenation{op-tical net-works semi-conduc-tor}


\begin{document}

\title{EDG++: Reliability-Aware Electron Density-Enhanced Molecular Geometry Learning}

\author{Hongxin Xiang, Siyu Wang, Zhixiang Cheng, Jun Xia, Xin Jin, Wenjie Du, Li Zeng, Hongbo Yang, and Xiangxiang Zeng,~\IEEEmembership{IEEE Senior Member}
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem \textit{(Hongxin Xiang and Siyu Wang are co-first authors.) (Corresponding authors: Hongbo Yang; Xiangxiang Zeng.)}
\IEEEcompsocthanksitem H. Xiang is with the College of Computer Science and Electronic Engineering, Hunan University, Changsha, China.
\IEEEcompsocthanksitem S. Wang is with the School of Life Sciences, East China Normal University, Shanghai, China.
\IEEEcompsocthanksitem Z. Cheng is with the College of Computer Science and Electronic Engineering, Hunan University, Changsha, China.
\IEEEcompsocthanksitem J. Xia is with the School of Engineering, Westlake University, Hangzhou, China.
\IEEEcompsocthanksitem X. Jin is with the Eastern Institute of Technology, Ningbo, China.
\IEEEcompsocthanksitem W. Du is with the University of Science and Technology of China, Hefei, China.
\IEEEcompsocthanksitem L. Zeng is with the College of Computer Science and Electronic Engineering, Hunan University, Changsha, China.
\IEEEcompsocthanksitem H. Yang is with the Institute of Reproduction and Development, Fudan University, Shanghai, China (e-mail: hongboyang@fudan.edu.cn).
\IEEEcompsocthanksitem X. Zeng is with the College of Computer Science and Electronic Engineering, Hunan University, Changsha, China (e-mail: xzeng@hnu.edu.cn).
}
}

\markboth{IEEE Transactions on Pattern Analysis and Machine Intelligence}%
{Xiang \MakeLowercase{\textit{et al.}}: EDG++: Reliability-Aware Electron Density-Enhanced Molecular Geometry Learning}

\IEEEtitleabstractindextext{
\input{sections_edgpp/abstract}
}

\maketitle

\IEEEdisplaynontitleabstractindextext
\IEEEpeerreviewmaketitle

\input{sections_edgpp/introduction}
\input{sections_edgpp/related_work}
\input{sections_edgpp/method}
\input{sections_edgpp/experiment}
\input{sections_edgpp/conclusion}

\section*{Acknowledgments}
This work was supported by the National Natural Science Foundation of China (grant nos. U22A2037, 62425204, 62122025, 62450002, 62432011), Grants of Ningbo 2023CX050011.

\bibliographystyle{IEEEtran}
\bibliography{edgpp_journal}

\newpage
\onecolumn
\appendices
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}
\input{sections_edgpp/appendix}

\vfill

\end{document}
